The \textit{Kepler} Smear Campaign: Light curves for 102 Very Bright Stars

### 2019-05-10 paper/ms.tex
smear campaign resubmitted

\author[0000-0003-2595-9114]{Benjamin J. S. Pope}
\affiliation{Center for Cosmology and Particle Physics, Department of Physics, New York University, 726 Broadway, New York, NY 10003, USA}
\affiliation{NASA Sagan Fellow}
\affiliation{Oxford Astrophysics, Denys Wilkinson Building, University of Oxford, OX1 3RH, Oxford, UK}

@@

\author[0000-0001-6637-5401]{Allyson Bieryla}
\affiliation{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138, USA}

\author[0000-0001-9911-7388]{David W. Latham}
\affiliation{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138, USA}

@@

\author[0000-0001-7402-3852]{Dominic W. Bowman}
\affiliation{Instituut voor Sterrenkunde, KU Leuven, Celestijnenlaan 200D, B-3001 Leuven, Belgium}

@@

% Abstract of the paper
\begin{abstract}
We present the first data release of the \kepler Smear Campaign, using collateral `smear' data obtained in the \kepler four-year mission to reconstruct light curves of 102~stars too bright to have been otherwise targeted. We describe the pipeline developed to extract and calibrate these light curves, and show that we attain photometric precision comparable to stars analyzed by the standard pipeline in the nominal \kepler mission. In this paper, aside from publishing the light curves of these stars, we focus on 66~red giants for which we detect solar-like oscillations, characterizing 33 of these in detail with spectroscopic chemical abundances and asteroseismic masses as benchmark stars. We also classify the whole sample, finding nearly all to be variable, with classical pulsations and binary effects. All source code, light curves, TRES spectra, and asteroseismic and stellar parameters are publicly available as a \kepler legacy sample. \href{https://github.com/benjaminpope/smearcampaign}{\faGithub}
\end{abstract}

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\keywords{asteroseismology -- techniques: photometric -- stars: variable: general
}

@@

We selected all stars on-silicon in \kepler with $Kp<9$ that were targeted for fewer than $8$ quarters. The majority of these were not previously targeted at all, but sixteen stars were to some extent observed conventionally; these are listed in Table~\ref{quarters}. A number of these lay at the edge of a detector, with the result that in some cadences the centroid of the star did not lie on the chip; light curves from these targets were found to be of extremely low quality and all of these stars were discarded. After applying these criteria we obtained a list of 102 targets, which are listed in Table~\ref{all_stars} with their \kepler magnitude $Kp$, together with their spectral type from SIMBAD, \gaia~DR2 apparent~$G$ magnitudes and $Bp-Rp$ colours, \gaia~DR2 calibrated distances from \citet{gaiadists}, variability classification and availability of TRES spectroscopy. The \kepler spacecraft rotates between quarters, so that it cycles through four orientation `seasons' each rotated from the last by $90^{\circ}$. Some stars were not on silicon for all seasons: we have only one season of HD~179394; two for HD~187277, HD~226754, V554~Lyr, and BD+47~2891; and three for BD+43~3064. The addition of our sample to the conventionally-observed stars makes the \kepler survey magnitude-complete down to $Kp=9$ for all stars on-silicon.

@@

Figure~\ref{hrdiagram} shows these stars on a colour-magnitude diagram using \gaia $Bp-Rp$ and absolute~$G$ magnitudes and \gaia~DR2 calibrated distances \citep{gaiadists}, overlaid on the \kepler sample from the Bedell \url{gaia-kepler.fun} crossmatch. The smear targets in this diagram selected to have higher apparent brightnesses than the general \kepler population, appear also to have higher intrinsic luminosities. While this could simply arise from being selected for their apparent brightness, it is {}worth considering whether this is because of a bias in their parallax measurements. While \gaia parallaxes for very bright stars can be subject to systematic error, we have compared to \hipparcos \citep{vanleeuwen07b}, and found close agreement for the brightest stars, with a scatter that increases with magnitude. We therefore suggest that parallax bias is not the reason for the smear sample sitting above the majority of the \kepler sample.

@@

\caption{\label{hrdiagram}
\gaia colour-magnitude diagram of the Smear Campaign stars (orange and teal) overlaid on the sample of \kepler stars with \gaia parallax $\text{SNR} > 25$ (black), using the Bedell \url{gaia-kepler.fun} crossmatch and \gaia~DR2 calibrated distances from \citet{gaiadists}. The smear sample includes giants and hot main-sequence stars. Those giants for which TRES spectroscopy have been obtained are highlighted in teal. An interactive version of this diagram is available as supplementary material from the journal or at \url{benjaminpope.github.io/data/cmd_smear.html}.}
\end{figure*}

@@

We can assess the importance of this contamination by considering differences between quarters. Because the Kepler spacecraft rotates $90^\circ$ between successive quarters, stars were observed on different CCD modules with the exception of stars on the central Module~13. Minor variations in the precise alignment of each CCD mean that the contribution from contaminating stars varies from quarter to quarter. Differences are clearer for Module~13, where contaminating stars will only be aligned along the same columns as a smear target every second quarter. We have therefore generated Lomb-Scargle periodograms \citep{lomb,scargle} of each light curve, after clipping for outliers. We consider only odd and even quarters separately, and also the full combined time series. In the great majority of cases they closely resemble one another, indicating that contamination is at worst a minor effect. In order to better quantify this, we computed the inner product of normalized periodograms of the odd and even quarters, each smoothed with a 3-element Gaussian kernel. If this overlap integral is 1, then the power spectra are identical; substantial departures from unity may be caused by real nonstationary or long-period stellar variation, noise, or gain or contamination differences between the seasons. We found that the distribution of overlaps (Figure~\ref{contamination2}) is strongly peaked around $\sim 0.91$, with a tail of 22 stars showing overlap $< 0.9$. We investigate these further, finding that in some of these cases  there was no obvious problem. For example, the classical pulsator HD~175841 showed amplitude changes of several pulsations but the overall distribution seemed very similar, from which we conclude that the variation is probably astrophysical.

In the case of HD~181878, a red giant on Module~13, there is clear and significant contamination from a star with several low-frequency pulsations, as is seen in Figure~\ref{contamination}. Likewise the light curve for HD 183383, which variously falls on Modules~8, 12, 14 and~18, shows different behaviour for different quarters: some parts are likely from an ellipsoidal variable with a period of 6.46 days, while other quarters are contaminated by the star RR Lyrae. Between seasons, there is an extra hump of power near the red giant oscillations in HD~175740; extra low frequency power in HD~180658; one coherent peak in  HD~182694; high frequency contamination in HD~181597 possibly from an EB; and a very significant difference in amplitude between seasons for BD~+39~3882. In other cases visual inspection does not show severe contamination, but in all cases we recommend that users of these light curves carefully check for differences between quarters, as well as investigating the full frame images for potential contaminants.

@@

@@

To estimate \Dnu, we divided the power spectrum by the granulation and noise models to obtain a signal-to-noise spectrum, and fit a sum of Lorentzians separated by mean large (\Dnu) and small (\dnu) separations to the part of this spectrum in the vicinity of \numax. For this dataset, \dnu is not constrained, but mean $\langle \Dnu \rangle$ is typically well-constrained and its posterior marginal distribution is well-represented by a single Gaussian.

@@

We determined the mass, radius, and age for the 33 red giants from their atmospheric and asteroseismic observables (see Table~\ref{astero_table}) using the BAyesian STellar Algorithm \citep[\textsc{basta}][]{silvaaguirre2015,silvaaguirre2017}. \textsc{basta} compares the observed properties with predictions from theoretical models of stellar evolution, in this case the recently updated BaSTI (a Bag of Stellar Tracks and Isochrones) stellar models and isochrones library \citep{Hidalgo:2018dy}. The isochrones include core overshooting with an efficiency of 0.20 times the pressure scale height as described in \citet{Hidalgo:2018dy}, but do not include diffusion or rotational mixing.

@@

To gauge the level of improvement in our understanding of these stars, in Figure~\ref{gaia_comparison} we plot the radii determined here against those from the \gaia~DR2 catalog determined by the stellar bolometric flux and parallax.  We also calculate \gaia-like stellar bolometric radii using \texttt{isoclassify} \citep{huber2017} using our new spectroscopic \teff measurements rather than those from \gaia~DR2, together with \gaia~DR2 parallaxes spectroscopic \logg, $Z$, and SIMBAD $V$. While not all of our targets have \gaia radii, we find that while there is overall agreement to within a few $\sigma$, the results from stellar modelling are consistently slightly larger than those from \gaia. This discrepancy goes away for most stars when we use our own \texttt{isoclassify} radii, suggesting that this is an effect of \teff calibration. Two stars are noticeably very different: BD+39~3577 has a precise \gaia radius of $9.14^{+0.25}_{-0.13}$~\rsun, but $24.78^{+0.88}_{-0.72}$~\rsun from modelling. It is unclear why this would be the case; it is possible that an unidentified binary companion has affected either the asteroseismic detection or parallax. Likewise BD+42~3150 has a \gaia radius of $15.70^{+0.52}_{-0.76}$~\rsun but $11.27^{+0.39}_{-0.41}$~\rsun from stellar modelling, but of our sample it has the lowest \gaia parallax over error at only 18.0, and this anomalously high value is likely due to noise. Agreement for large-radius ($>30 \rsun$) stars is somewhat poorer, even though the \gaia parallax-over-error is apparently adequate. This dispersion, unlike for medium radius stars, is more pronounced for the \texttt{isoclassify} radii than for \gaia~DR2, suggesting that our $V$ band bolometric corrections for these more yellow (\gaia $Bp-Rp \sim 0.25$) stars are insufficiently accurate.

@@

\caption{\label{gaia_comparison}
A comparison of the stellar radii determined here from asteroseismology and spectroscopy to those from the \gaia~DR2 catalogue and from our own calculations based on \gaia parallaxes and TRES spectroscopy. There is overall good agreement except for very large radii, and except for BD+39~3577 (marked).}
\end{figure}

@@

The coherent g-mode pulsations in samples of B, A, and F stars observed by \kepler previously showed these stars to be near-rigid rotators \citep{kurtz2014,saio15,triana15,vanreeth15,vanreeth16,vanreeth18,murphy16,schmid16,moravveji16,ouazzani17,papics17,aerts17,szewczuk18,2018arXiv180907779A,2018A&A...618A..47C,2019MNRAS.482.1757L}. These studies cover about 100 stars so far and many more are to come. For 37 of the F-type pulsators among those, asteroseismic modelling of the g modes led to their masses, ages, core rotation and core mass with relative precisions of about 10\% \citep{2019MNRAS.tmp..495M}. The vast majority of B-type intermediate-mass stars observed byKepler have yet to be subjected to in-depth asteroseismic analyses and modelling of their interior properties. However, the vast majority of intermediate-mass stars observed by Kepler have yet to be subjected to in-depth asteroseismic analyses and modelling of their interior properties. One of the valuable outputs of our current work includes the reduced light curves of several early-B stars, which were only scarcely targeted in the nominal \kepler mission. The few that were monitored did not reveal suitable oscillation frequency patterns to achieve a unique mode identification, which is a requirement to perform asteroseismic modelling. The investigation of pulsation modes in high-mass stars using high-quality \kepler smear data combined with high-precision spectroscopy to identify the modes \citep[Chapter 6]{aertsbook} is an exciting prospect for asteroseismology, as the interior physics of these stars are largely unknown, yet they play a pivotal role in stellar and galactic evolution. The in-depth asteroseismic analysis of the smear data for the~B~stars will be the subject of future work.

@@

Several stars in the sample show the `hump-and-spike' morphology in their power spectra \citep[a broad `hump' of low-amplitude oscillations dominated by one high amplitude coherent oscillation toward the high frequency end of this band;][]{2013MNRAS.431.2240B,2014MNRAS.441.3543B,2017MNRAS.467.1830B,2018MNRAS.474.2774S}: these are marked `H+S' in Table~\ref{stellar_props}.
%HD~186155 (HR~7495), 14~Cyg (HD~185872, HR~7483), HD~189178 (HR~7628), HD~183362 (HR~7403), and HD~184787. 
Of these, HD~186155 and 14~Cyg are the third-- and sixth--brightest stars on silicon, making these the brightest stars that show this effect. The identification for HD~189178 is tentative, as the spectrum also shows evidence of SPB pulsations, and for HD~183362 for $\gamma$\,Dor pulsations, while for HD~184787 there is long term variability consistent with contamination. The other hump-and-spike identifications seem secure. \citet{2018MNRAS.474.2774S} have recently interpreted the hump-and-spike power spectra as evidence for Rossby modes. The F5 star HD~186155, identified by SIMBAD as having a giant spectral type of F5II-III, is shown by its \gaia distance to in fact lie on the main-sequence. A detailed study of these stars will be presented by Antoci et al., in prep.

@@

@@

This work was performed in part under contract with the Jet Propulsion Laboratory (JPL) funded by NASA through the Sagan Fellowship Program executed by the NASA Exoplanet Science Institute. BJSP also acknowledges support from Balliol College and the Clarendon Fund. DH acknowledges support by the National Aeronautics and Space Administration through the K2 Guest Observer Program (NNX17AF76G, 80NSSC19K0108, 80NSSC18K0362) and the National Science Foundation (AST-1717000). TRW acknowledges the support of the Australian Research Council (grant DP150100250). TRW and VSA acknowledge
the support of the Villum Foundation (research grant 10118). DWL acknowledges partial support from the Kepler Extended Mission under NASA Cooperative Agreement NNX13AB58A with the Smithsonian Astrophysical Observatory. The research leading to these results has received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (grant agreement No670519: MAMSIE). VSA acknowledges support the Independent Research Fund Denmark (Research grant 7027-00096B). Funding for the Stellar Astrophysics Centre is provided by The Danish National Research Foundation (Grant agreement No.~DNRF106). PJ acknowledges FONDECYT Iniciaci\'on grant 11170174.

@@

This work has made use of data from the European Space Agency (ESA) mission
{\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed by the {\it Gaia}
Data Processing and Analysis Consortium (DPAC,
\url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding for the DPAC
has been provided by national institutions, in particular the institutions
participating in the {\it Gaia} Multilateral Agreement. This work has made use of the \url{gaia-kepler.fun} crossmatch database created by Megan Bedell.

This research made use of NASA's Astrophysics Data System; the SIMBAD database, operated at CDS, Strasbourg, France; the IPython package \citep{PER-GRA:2007}; SciPy \citep{jones_scipy_2001}; and Astropy, a community-developed core Python package for Astronomy \citep{astropy}. Some of the data presented in this paper were obtained from the Mikulski Archive for Space Telescopes (MAST). STScI is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS5-26555. Support for MAST for non-HST data is provided by the NASA Office of Space Science via grant NNX13AC07G and by other grants and contracts. We acknowledge the support of the Group of Eight universities and the German Academic Exchange Service through the Go8 Australia-Germany Joint Research Co-operation Scheme.

@@

>>>>

\author[0000-0003-2595-9114]{Benjamin J. S. Pope}
\affiliation{Center for Cosmology and Particle Physics, Department of Physics, New York University, 726 Broadway, New York, NY 10003, USA}
\affiliation{Center for Data Science, New York University, 60 Fifth Ave, New York, NY 10011, USA}
\affiliation{NASA Sagan Fellow}
\affiliation{Oxford Astrophysics, Denys Wilkinson Building, University of Oxford, OX1 3RH, Oxford, UK}

@@

\author[0000-0001-6637-5401]{Allyson Bieryla}
\affiliation{Center for Astrophysics | Harvard \& Smithsonian, 60 Garden Street, Cambridge, MA 02138, USA}

\author[0000-0001-9911-7388]{David W. Latham}
\affiliation{Center for Astrophysics | Harvard \& Smithsonian, 60 Garden Street, Cambridge, MA 02138, USA}

@@

\author[0000-0001-7402-3852]{Dominic M. Bowman}
\affiliation{Instituut voor Sterrenkunde, KU Leuven, Celestijnenlaan 200D, B-3001 Leuven, Belgium}

@@

% Abstract of the paper
\begin{abstract}
We present the first data release of the \kepler Smear Campaign, using collateral `smear' data obtained in the \kepler four-year mission to reconstruct light curves of 102~stars too bright to have been otherwise targeted. We describe the pipeline developed to extract and calibrate these light curves, and show that we attain photometric precision comparable to stars analyzed by the standard pipeline in the nominal \kepler mission. In this paper, aside from publishing the light curves of these stars, we focus on 66~red giants for which we detect solar-like oscillations, characterizing 33 of these in detail with spectroscopic chemical abundances and asteroseismic masses as benchmark stars. We also classify the whole sample, finding nearly all to be variable, with classical pulsations and binary effects. All source code, light curves, TRES spectra, and asteroseismic and stellar parameters are publicly available as a \kepler legacy sample. \href{https://github.com/benjaminpope/smearcampaign}{\color{linkcolor}\faGithub}
\end{abstract}

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\keywords{asteroseismology -- techniques: photometric -- stars: variable: general -- 
stars: early-type -- stars: red giants -- stars: rotation}

@@

We selected all stars on-silicon in \kepler with $Kp<9$ that were targeted for fewer than $8$ quarters. The majority of these were not previously targeted at all, but sixteen stars were to some extent observed conventionally; these are listed in Table~\ref{quarters}. A number of these lay at the edge of a detector, with the result that in some cadences the centroid of the star did not lie on the chip; light curves from these targets were found to be of extremely low quality and all of these stars were discarded. After applying these criteria we obtained a list of 102 targets, which are listed in Table~\ref{all_stars} with their \kepler magnitude $Kp$, together with their spectral type from SIMBAD, \gaia~DR2 apparent~$G$ magnitudes and $Bp-Rp$ colors, \gaia~DR2 calibrated distances from \citet{gaiadists}, variability classification and availability of TRES spectroscopy. It should be noted that $Bp-Rp$ colours are not calibrated for reddening and are therefore not a precise measure of stellar temperature. The \kepler spacecraft rotates between quarters, so that it cycles through four orientation `seasons' each rotated from the last by $90^{\circ}$. Some stars were not on silicon for all seasons: we have only one season of HD~179394; two for HD~187277, HD~226754, V554~Lyr, and BD+47~2891; and three for BD+43~3064. The addition of our sample to the conventionally-observed stars makes the \kepler survey magnitude-complete down to $Kp=9$ for all stars on-silicon.

@@

Figure~\ref{hrdiagram} shows these stars on a colour-magnitude diagram using \gaia $Bp-Rp$ and absolute~$G$ magnitudes and \gaia~DR2 calibrated distances \citep{gaiadists}, overlaid on the \kepler sample from the Bedell \href{https://gaia-kepler.fun}{\nolinkurl{gaia-kepler.fun}} crossmatch. The smear targets in this diagram selected to have higher apparent brightnesses than the general \kepler population, appear also to have higher intrinsic luminosities. While this could simply arise from being selected for their apparent brightness, it is {}worth considering whether this is because of a bias in their parallax measurements. While \gaia parallaxes for very bright stars can be subject to systematic error, we have compared to \hipparcos \citep{vanleeuwen07b}, and found close agreement for the brightest stars, with a scatter that increases with magnitude. We therefore suggest that parallax bias is not the reason for the smear sample sitting above the majority of the \kepler sample.

@@

\caption{\label{hrdiagram}
\gaia colour-magnitude diagram of the Smear Campaign stars (orange and teal) overlaid on the sample of \kepler stars with \gaia parallax $\text{SNR} > 25$ (black), using the Bedell \href{https://gaia-kepler.fun}{\nolinkurl{gaia-kepler.fun}} crossmatch and \gaia~DR2 calibrated distances from \citet{gaiadists}. The smear sample includes giants and hot main-sequence stars. Those giants for which TRES spectroscopy have been obtained are highlighted in teal. Three stars discussed in the text are marked with $\star$ symbols. An interactive version of this diagram is available as supplementary material from the journal or at  \href{https://benjaminpope.github.io/data/cmd_smear.html}{\nolinkurl{benjaminpope.github.io/data/cmd_smear.html}}.}
\end{figure*}

@@

We can assess the importance of this contamination by considering differences between quarters. Because the Kepler spacecraft rotates $90^\circ$ between successive quarters, stars were observed on different CCD modules with the exception of stars on the central Module~13. Minor variations in the precise alignment of each CCD mean that the contribution from contaminating stars varies from quarter to quarter. Differences are clearer for Module~13, where contaminating stars will only be aligned along the same columns as a smear target every second quarter. We have therefore generated Lomb-Scargle periodograms \citep{lomb,scargle} of each light curve, after clipping for outliers. We consider only odd and even quarters separately, and also the full combined time series. In the great majority of cases they closely resemble one another, indicating that contamination is at worst a minor effect. In order to better quantify this, we computed the inner product of normalized periodograms of the odd and even quarters, each smoothed with a 3-element Gaussian kernel. If this overlap integral is 1, then the power spectra are identical; substantial departures from unity may be caused by real nonstationary or long-period stellar variation, noise, or gain or contamination differences between the seasons. We found that the distribution of overlaps (Figure~\ref{contamination2}) is strongly peaked around $\sim 0.91$, with a tail of 22 stars showing overlap $< 0.9$. We investigate these further, finding that in some of these cases  there was no obvious problem. For example, the classical pulsator HD~175841 showed amplitude changes of several pulsations but the overall distribution seemed very similar, from which we conclude that the variation is probably astrophysical \citep[as in][]{2016MNRAS.460.1970B}.

In the case of HD~181878, a red giant on Module~13, there is clear and significant contamination from a star with several low-frequency pulsations, as is seen in Figure~\ref{contamination}. Likewise the light curve for HD 183383, which variously falls on Modules~8, 12, 14 and~18, shows different behaviour for different quarters: some parts are likely from an ellipsoidal variable with a period of 6.46 days, while other quarters are contaminated by the star RR~Lyrae. The effects of this contamination in the time domain are shown in Figure~\ref{contamination_timeseries}: there is very little discernable effect for HD~181878 by eye, whereas the RR~Lyr contamination in HD~183383 is readily apparent. Between seasons, there is an extra hump of power near the red giant oscillations in HD~175740; extra low frequency power in HD~180658; one coherent peak in  HD~182694; high frequency contamination in HD~181597 possibly from an EB; and a very significant difference in amplitude between seasons for BD~+39~3882. In other cases visual inspection does not show severe contamination, but in all cases we recommend that users of these light curves carefully check for differences between quarters, as well as investigating the full frame images for potential contaminants.

@@

\begin{figure}
\plotone{contam_timeseries.pdf}
\caption{\label{contamination_timeseries}
Time series of Quarters 12-13 of HD~181778 and HD~183383, both of which show contamination. For HD~181778, contamination is not apparent to the eye in the time series, but Figure~\ref{contamination} showed that in its power spectrum there is a significant effect from a coherent oscillator. Meanwhile in HD~183383, even quarters show easily visible contamination from the star RR~Lyr, some quarters worse than others, while odd quarters show low amplitude coherent variability consistent with an ellipsoidal variable.} 
\end{figure}

@@

To estimate \Dnu, we divided the power spectrum by the granulation and noise models to obtain a signal-to-noise spectrum, and fit a sum of Lorentzians separated by mean large (\Dnu) and small (\dnu) separations to the part of this spectrum in the vicinity of \numax. For this dataset, \dnu is not constrained, but mean $\langle \Dnu \rangle$ is typically well-constrained and its posterior marginal distribution is well-represented by a single Gaussian. We fit and report also the dimensionless parameter $\epsilon$ is the offset of the lowest frequency in the comb of p-modes from zero frequency in units of $\Dnu$.

@@

We determined the mass, radius, and age for the 33 red giants from their atmospheric and asteroseismic observables (see Table~\ref{astero_table}) using the BAyesian STellar Algorithm \citep[\textsc{basta}][]{silvaaguirre2015,silvaaguirre2017}. \textsc{basta} compares the observed properties (\teff, \feh, \logg, \Dnu, and \numax) with predictions from theoretical models of stellar evolution, in this case the recently updated BaSTI (a Bag of Stellar Tracks and Isochrones) stellar models and isochrones library \citep{Hidalgo:2018dy}. The isochrones include core overshooting with an efficiency of 0.20 times the pressure scale height as described in \citet{Hidalgo:2018dy}, but do not include diffusion or rotational mixing.

@@

To gauge the level of improvement in our understanding of these stars, in Figure~\ref{gaia_comparison} we plot the radii determined here against those from the \gaia~DR2 catalog determined by the stellar bolometric flux and parallax. 
We also calculate \gaia-like stellar bolometric radii using the software \texttt{isoclassify} \citep{huber2017}, using as our input \teff values our new spectroscopic \teff, \feh, and \logg measurements rather than those from \gaia~DR2, together with \gaia~DR2 parallaxes, and SIMBAD $V$. While not all of our targets have radii in the \gaia catalogs, for those that do we find that there is overall agreement to within a few $\sigma$, but that the results from stellar modelling are consistently slightly larger than those from \gaia. 
This discrepancy goes away for most stars when we use our own \texttt{isoclassify} radii, suggesting that this is an effect of \teff calibration. Two stars are noticeably very different: BD+39~3577 has a precise \gaia radius of $9.14^{+0.25}_{-0.13}$~\rsun, but $24.78^{+0.88}_{-0.72}$~\rsun from modelling. It is unclear why this would be the case; it is possible that an unidentified binary companion has affected either the asteroseismic detection or parallax. Likewise BD+42~3150 has a \gaia radius of $15.70^{+0.52}_{-0.76}$~\rsun but $11.27^{+0.39}_{-0.41}$~\rsun from stellar modelling, but of our sample it has the lowest \gaia parallax over error at only 18.0, and this anomalously high value is likely due to noise. Agreement for large-radius ($>30 \rsun$) stars is somewhat poorer, even though the \gaia parallax-over-error is apparently adequate. This dispersion, unlike for medium radius stars, is more pronounced for the \texttt{isoclassify} radii than for \gaia~DR2, suggesting that our $V$ band bolometric corrections for these more yellow (\gaia $Bp-Rp \sim 0.25$) stars are insufficiently accurate.

@@

\caption{\label{gaia_comparison}
A comparison of the stellar radii determined here from asteroseismology and spectroscopy to those from the \gaia~DR2 catalogue ($y$-axis) and from our own calculations based on \gaia parallaxes and TRES spectroscopy ($x$-axis). Blue points are from \gaia measurements explicitly, and orange points \gaia-like calculations using \texttt{isoclassify} \citep{huber2017} and substituting own $T_{eff}$ measurements rather than those from \gaia. The green line overlaid shows a 1:1 relation. There is overall good agreement except for very large radii, and except for BD+39~3577 (marked).}
\end{figure}

@@

The coherent g-mode pulsations in samples of B, A, and F stars observed by \kepler previously showed these stars to be near-rigid rotators \citep{kurtz2014,saio15,triana15,vanreeth15,vanreeth16,vanreeth18,murphy16,schmid16,moravveji16,ouazzani17,papics17,aerts17,szewczuk18,2018arXiv180907779A,2018A&A...618A..47C,2019MNRAS.482.1757L}. These studies cover about 100 stars so far and many more are to come. For 37 of the F-type pulsators among those, asteroseismic modelling of the g modes led to their masses, ages, core rotation and core mass with relative precisions of about 10\% \citep{2019MNRAS.tmp..495M}. However, the vast majority of intermediate-mass stars observed by Kepler have yet to be subjected to in-depth asteroseismic analyses and modelling of their interior properties. One of the valuable outputs of our current work includes the reduced light curves of several early-B stars, which were only scarcely targeted in the nominal \kepler mission. The few that were monitored did not reveal suitable oscillation frequency patterns to achieve a unique mode identification, which is a requirement to perform asteroseismic modelling. The investigation of pulsation modes in high-mass stars using high-quality \kepler smear data combined with high-precision spectroscopy to identify the modes \citep[Chapter 6]{aertsbook} is an exciting prospect for asteroseismology, as the interior physics of these stars are largely unknown \citep[e.g.][]{2019arXiv190502120B}, yet they play a pivotal role in stellar and galactic evolution. The in-depth asteroseismic analysis of the smear data for the~B~stars will be the subject of future work.

@@

Several stars in the sample show the `hump-and-spike' morphology in their power spectra \citep[a broad `hump' of low-amplitude oscillations dominated by one high amplitude coherent oscillation toward the high frequency end of this band;][]{2013MNRAS.431.2240B,2014MNRAS.441.3543B,2017MNRAS.467.1830B}. \citet{2018MNRAS.474.2774S} have recently interpreted the hump-and-spike power spectra as evidence for Rossby modes.
%HD~186155 (HR~7495), 14~Cyg (HD~185872, HR~7483), HD~189178 (HR~7628), HD~183362 (HR~7403), and HD~184787. 
These stars are marked `H+S' in Table~\ref{stellar_props}. Of these, HD~186155 and 14~Cyg are the third-- and sixth--brightest stars on silicon, making these the brightest stars that show this effect. The identification for HD~189178 is tentative, as the power spectrum also shows evidence of SPB pulsations. This is likewise the case for HD~183362 which shows $\gamma$\,Dor pulsations, and for HD~184787 there is long-term variability consistent with contamination. The other hump-and-spike identifications seem secure. The F5 star HD~186155, identified by SIMBAD as having a giant spectral type of F5II-III, is shown by its \gaia distance to in fact lie on the main-sequence. A detailed study of these stars will be presented by Antoci et al., in prep.

@@

\begin{figure}
\plotone{humpandspike.pdf}

\caption{\label{hs_fig}
Lomb-Scargle periodograms in normalized amplitude of three `Hump and Spike' stars: HD~189718, HD~184787, and HD~183362, with the `hump' features highlighted with red ellipses.}
\end{figure}

@@

This work was performed in part under contract with the Jet Propulsion Laboratory (JPL) funded by NASA through the Sagan Fellowship Program executed by the NASA Exoplanet Science Institute. BJSP also acknowledges support from Balliol College and the Clarendon Fund. DH acknowledges support by the National Aeronautics and Space Administration through the K2 Guest Observer Program (NNX17AF76G, 80NSSC19K0108, 80NSSC18K0362) and the National Science Foundation (AST-1717000). TRW acknowledges the support of the Australian Research Council (grant DP150100250). TRW and VSA acknowledge
the support of the Villum Foundation (research grant 10118). DWL acknowledges partial support from the Kepler Extended Mission under NASA Cooperative Agreement NNX13AB58A with the Smithsonian Astrophysical Observatory. The research leading to these results has received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (grant agreement N$^\circ$670519: MAMSIE). VSA acknowledges support the Independent Research Fund Denmark (Research grant 7027-00096B). Funding for the Stellar Astrophysics Centre is provided by The Danish National Research Foundation (Grant agreement No.~DNRF106). PJ acknowledges FONDECYT Iniciaci\'on grant 11170174.

@@

This work has made use of data from the European Space Agency (ESA) mission
{\it Gaia} (\href{https://www.cosmos.esa.int/gaia}{\nolinkurl{cosmos.esa.int/gaia}}), processed by the {\it Gaia}
Data Processing and Analysis Consortium (DPAC, \href{https://www.cosmos.esa.int/web/gaia/dpac/consortium}{\nolinkurl{cosmos.esa.int/web/gaia/dpac/consortium}}). Funding for the DPAC
has been provided by national institutions, in particular the institutions
participating in the {\it Gaia} Multilateral Agreement. This work has made use of the \href{https://gaia-kepler.fun}{\nolinkurl{gaia-kepler.fun}} crossmatch database created by Megan Bedell.

This research made use of NASA's Astrophysics Data System; the SIMBAD database, operated at CDS, Strasbourg, France. Some of the data presented in this paper were obtained from the Mikulski Archive for Space Telescopes (MAST). STScI is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS5-26555. Support for MAST for non-HST data is provided by the NASA Office of Space Science via grant NNX13AC07G and by other grants and contracts. We acknowledge the support of the Group of Eight universities and the German Academic Exchange Service through the Go8 Australia-Germany Joint Research Co-operation Scheme.

\software{IPython  \citep{PER-GRA:2007}; SciPy \citep{jones_scipy_2001}; and Astropy, a community-developed core Python package for Astronomy \citep{astropy}.}

@@

\appendix
